---
title: "Public Funding in Germany as of January 2023"
author: "drfetz"
date: "2022-12-06"
output: html_document
---

```{r load-packages, include=FALSE}
library(tidyverse)
library(dplyr)
library(magrittr)
library(knitr)
library(DT)
library(kableExtra)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preface

The present report deals with public funding in Germany. Only **Verbundprojekte** - projects with more than two participating entities - have been assessed.
The data is publicly available via: <https://foerderportal.bund.de/foekat/jsp/SucheAction.do>. 

## Funding by ressort

BMBF = Bundesministerium für Bildung und Forschung, Federal ministry of education and research;
BMDV = Bundesministerium für Digitales und Verkehr, Federal ministry of digital and transport;
BMEL = Bundesministerium für Ernährung und Landwirtschaft, Federal ministry of food and agriculture;
BMWK = Bundesministerium für Wirtschaft und Klimaschutz, Federal ministry of economic affairs and climate action.
According to the website, each ministry is individually responsible for providing accurate data.

```{r data, include=FALSE}
foerder_db <- read.csv(file = "Foerderdatenbank_GER_clean.csv", 
                       header = TRUE)

```

```{r variables, include=FALSE}
# Variables

# format number as numeric

foerder_db$Fördersumme.in.EUR <- as.numeric(foerder_db$Fördersumme.in.EUR)

# format dates

foerder_db$date_start <- as.Date(foerder_db$Laufzeit.von, format = "%d.%m.%y")

foerder_db$date_end <- as.Date(foerder_db$Laufzeit.bis, format = "%d.%m.%y")

# project duration

foerder_db$duration <- (foerder_db$date_end - foerder_db$date_start)
```


```{r overview, echo=FALSE}

foerder_db %>%
  group_by(Ressort) %>%
  summarise(Number_Fundings = prettyNum(n(),big.mark = ",", scientific = F),
            Number_Orgs = prettyNum(n_distinct(Zuwendungsempfänger),big.mark = ",", scientific = F),
            Number_Cities = prettyNum(n_distinct(Ort),big.mark = ",", scientific = F),
            Funding_Ave = prettyNum(mean(Fördersumme.in.EUR),big.mark = ",", scientific = F),
            Funding_Total = prettyNum(sum(Fördersumme.in.EUR), big.mark = ",", scientific = F),
            Duration_Ave = prettyNum(mean(duration, na.rm = T),big.mark = ",", scientific = F),
            From = min(date_start, na.rm = T),
            To = max(date_start, na.rm = T)
  ) %>%
kbl() %>%
  kable_styling()

```

## Most funded organizations and entities in innovation and technology research

The table displays entity names, the count of fundings, the average funding and the total funding they received given the provided data.

```{r orgs and entities, echo=FALSE}

foerder_tech_db <- foerder_db %>%
  filter(Förderprofil == "Technologie- und Innovationsförderung" & Fördersumme.in.EUR > 0) %>%
  group_by(Zuwendungsempfänger) %>%
  summarise(Fundings = prettyNum(n(),big.mark = ",", scientific = F),
            Funding_Ave = prettyNum(mean(Fördersumme.in.EUR),big.mark = ",", scientific = F),
            Funding_Total = prettyNum(sum(Fördersumme.in.EUR), big.mark = ",", scientific = F)
  )

datatable(foerder_tech_db)


```

## Funding by federal state

The table displays entity names, the count of fundings, the average funding and the total funding they received given the provided data.

```{r federal state, echo=FALSE}

foerder_federal_db <- foerder_db %>%
  filter(Förderprofil == "Technologie- und Innovationsförderung" & Fördersumme.in.EUR > 0) %>%
  group_by(Bundesland) %>%
  summarise(Fundings = prettyNum(n(),big.mark = ",", scientific = F),
            Funding_Ave = prettyNum(mean(Fördersumme.in.EUR),big.mark = ",", scientific = F),
            Funding_Total = prettyNum(sum(Fördersumme.in.EUR), big.mark = ",", scientific = F)
  )

datatable(foerder_federal_db)


```